---
title: "Week 2 AED Markdown (Asdos)"
author: "Assistant Lecturer-A(Bondan and Kevin)"
date: "3/16/2021"
output: html_document
---

# Bonjour! AED-A Class
## Dipelajari YA!!!

```{r}
getwd()
setwd("C:/Users/bonda/OneDrive/Documents/MATKUL STATISTIK/Asdos AED Materi/Week 2")
```

## 1. Pie Chart
In R the pie chart is created using the pie() function which takes positive numbers as a vector input. The additional parameters are used to control labels, color, title etc.

###Syntax
```
pie(x, labels, radius, main, col, clockwise)
```

Following is the description of the parameters used −

* x is a vector containing the numeric values used in the pie chart.

* labels is used to give description to the slices.

* radius indicates the radius of the circle of the pie chart.(value between −1 and +1).

* main indicates the title of the chart.

* col indicates the color palette.

 *clockwise is a logical value indicating if the slices are drawn clockwise or anti clockwise.

#### Simple Pie Chart
```{r}
slices <- c(10, 12,4, 16, 8)
lbls <- c("US", "UK", "Australia", "Germany", "France")
pie(slices, labels = lbls, main="Pie Chart of Countries")
```
#### How To Set Specific Color in Pie Chart
I want to give colors to the piechart. I used. I want to give red color for apple, orange color for orange and blue color for grape etc. But my pie chart looks different.

```{r}
chem <- c("Apel","Jeruk","Anggur Merah","Pisang","Kedondong")
vol <- c(90,50,100,40,20)
pie(x=vol, labels = chem, radius = 1,main = "Pie chart for chemical production", col=c("red","orange","maroon","yellow","black"),clockwise = T)
```
 
```{r}
employee <- read.csv("mtcars.csv", TRUE, sep = ",")
data <- aggregate(mtcars$carb, 
                  by=list(mtcars$gear), FUN=sum)
print(data)

pie(data$x, data$Group.1, col = rainbow(length(data$x)))
```


## 2. Bar Plot
#### Simple Bar Plot
# Simple Bar Plot
```{r}
counts <- table(mtcars$gear)
barplot(counts, main="Car Distribution",
   xlab="Number of Gears")
```
Horizontal Bar Plot
```{r}
counts <- table(mtcars$gear)
barplot(counts, main="Car Distribution",
   xlab="Number of Gears")
```
Stacked Bar Plot
```{r}
# Stacked Bar Plot with Colors and Legend
counts <- table(mtcars$vs, mtcars$gear)
barplot(counts, main="Car Distribution by Gears and VS",
  xlab="Number of Gears", col=c("darkblue","red"),
  legend = rownames(counts))
```
Group Bar Plot
```{r}
# Stacked Bar Plot with Colors and Legend
# Grouped Bar Plot
counts <- table(mtcars$vs, mtcars$gear)
barplot(counts, main="Car Distribution by Gears and VS",
  xlab="Number of Gears", col=c("darkblue","red"),
  legend = rownames(counts), beside=TRUE)
```


