---
title: "Week 4 Material"
author: "Assistant Lecturer-A (Bondan and Kevin)"
date: "3/31/2021"
output: html_document
---

# Selamat Siang Semuanya
## Minta Tolong Dipelajari Ya!

### MATERIAL FOR TODAY:
**Materi R For Today Learning**

- Phi

- Cramer's V

- Stacked & Grouped barplot

- Pearson correlation

---
_Variable MtCars :_

mpg = Miles/(US) gallon

cyl = Number of cylinders

disp = Displacement (cu.in.)

hp = Gross horsepower

drat = Rear axle ratio

wt = Weight (1000 lbs)

qsec = 1/4 mile time

vs = Engine (0 = V-shaped, 1 = straight)

am = Transmission (0 = automatic, 1 = manual)

gear = Number of forward gears

```{r}
packages = c('rcompanion', 'vcd', 'psych', 'DescTools', 'epitools')
lapply(packages, library, character.only = TRUE)
```


## Contoh Memakai Data MTCARS
```{r}
data(mtcars)
head(mtcars)
```
```{r}
mtcars2 <- within(mtcars, {
   vs <- factor(vs, labels = c("V-shaped", "Straight"))
   am <- factor(am, labels = c("Automatic", "Manual"))
   cyl  <- ordered(cyl)
   gear <- ordered(gear)
   carb <- ordered(carb)
})
head(mtcars2)
```
```{r}
summary(mtcars)
```
```{r}
summary(mtcars2)
```


## Phi 
## Data PDF Hal. 775
```{r}
Input =("
Opinion      Male Female
  Agree      75   25
  Disagree   25   25
")
Matrix.2 = as.matrix(read.table(textConnection(Input),
                                header=TRUE,
                                row.names=1))
Matrix.2
```
```{r}
library(psych)
```
```{r}
phi(Matrix.2,
    digits = 4)
```
```{r}
library(DescTools)
```

```{r}
Phi(Matrix.2)
```


## Cramer's $V$
## Data Buatan Sendiri

```{r}
Input =("
County               Pass   Fail
Bloom                21      5
Cobblestone           6     11
Dougal                7      8
Heimlich             27      5
")

Matrix = as.matrix(read.table(textConnection(Input),
                              header=TRUE,
                              row.names=1))

Matrix
```
```{r}
library(rcompanion)
```
```{r}
cramerV(Matrix,
        digits=4)
```
```{r}
library(vcd)
```
```{r}
assocstats(Matrix)
```
```{r}
library(DescTools)
```
```{r}
CramerV(Matrix,conf.level=0.95)
```


## Confident Contigency
```{r}
assocstats(Matrix)
```

## Visualisasi
```{r}
barplot(Matrix,
        main = 'The state that conducts the national exam',
        col=c('#184E77','#1A759F','#d9ed92', '#99d98c'), 
        border="white", 
        xlab="Result",
        ylim = c(0, 70))

legend(x = 2, y = 70, legend = c('County',      
'Bloom',       
'Cobblestone', 
'Dougal',      
'Heimlich'),
       col = c('#184E77','#1A759F','#d9ed92', '#99d98c'),
       bty = 'n',
       pch = c(19,19,19,19),
       cex = 0.55,
       text.col = '#1e6091'
)
        
```
```{r}
barplot(Matrix,
        main = 'The state that conducts the national exam',
        col=c('#184E77','#1A759F','#d9ed92', '#99d98c'), 
        border="white", 
        xlab="Result",
        beside = T,
        ylim = c(0, 70))

legend(x = 7, y = 70, legend = c('County',      
'Bloom',       
'Cobblestone', 
'Dougal',      
'Heimlich'),
       col = c('#184E77','#1A759F','#d9ed92', '#99d98c'),
       bty = 1,
       pch = c(19,19,19,19),
       cex = 0.6,
       text.col = '#1e6091'
)
```

## Pearson Correlation
```{r}
pairs.panels(mtcars2[,c(3:7)], 
             method = 'pearson', # Metode Korelasi Pearson
             hist.col = '#34A0A4',
             density = TRUE,  
             ellipses = TRUE, # menampilkan elips dari korelasi
             main = 'Pair plot of disp, hp, drat, wt, qsec')
```













